A Comparison of Graph Processing Systems

### 2020-09-23 documentation/paper/main.tex
kleine Korrekturen

\begin{abstract}
Graphs are growing fast and are becoming increasingly popular in many different domains.
There are several different frameworks that make it easy to write graph algorithms.
They often use different approaches and have significant performance differences on different graphs.
In this paper we compare some state-of-the-art non-uniform memory access (NUMA) aware systems in terms of performance, both on real world and synthetic graphs.
Therefore we consider the three algorithms single-source shortest-path (SSSP), breath-first search (BFS) and PageRrank (PR).
We compare not only the time the algorithms indicate that they actually need to compute, but also the time they actually run and consume resources, and the resulting overhead time.
\end{abstract}

>>>>

\begin{abstract}
Graphs are growing fast and are becoming increasingly popular in many different domains.
There are several different frameworks that make it easy to write graph algorithms.
They often use different approaches and have significant performance differences on different graphs.
In this paper we compare some state-of-the-art non-uniform memory access (NUMA) aware systems in terms of performance, both on real world and synthetic graphs.
Therefore, we consider the three algorithms Single-Source Shortest-Paths (SSSP), Breadth-First Search (BFS) and PageRank (PR).
We compare not only the time the frameworks indicate, they need to compute, but also the time they actually run and consume resources, and the resulting overhead time.
\end{abstract}
